---
title: "Alcohol vs Seat choice"
author: "Aeilani Felix"
date: "Spring 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question: Is there a difference between the alcohol consumed between the row you choose to sit in??

# Introduction 

Is the average amount consumed per week different for the different seating rows?

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows.   

# Methods 

Data is from the UCDavis.csv

We are trying to predict alcohol consumption based on row alcohol ~ Seat

Alcohol is a numeric variable 
Seat is a categorical variable 

So we use the numerical~cat helper file

# Description 
## Graphical description 

```{r}
boxplot(alcohol~Seat,data=davisdata)
```

This boxplot shows that students who sit in the back row tend to drink more.

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```

## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  According to the box plot, it shows that more alcohol consumers are in the back seats.
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

## Inferential Tests

## Conclusions


