---
title: "Alcohol vs Seat choice"
author: "Aeilani Felix"
date: "Spring 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question: Is there a difference between the alcohol consumed between the row you choose to sit in??

# Introduction 

Is the average amount consumed per week different for the different seating rows?

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows.   

# Methods 

Data is from the UCDavis.csv

We are trying to predict alcohol consumption based on row alcohol ~ Seat

Alcohol is a numeric variable 
Seat is a categorical variable 

So we use the numerical~cat helper file

# Description 
## Graphical description 

```{r}
boxplot(alcohol~Seat,data=davisdata)
```

This boxplot shows that students who sit in the back row tend to drink more.

## Numerical description

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

According to this numerical description it shows that the median for the backseats 3.5, the front seat consumption was 0.0, and the middle seat was 1.0. So apparently the people who drink more sit in the back.

## Inferential 

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

In this case, the p-value is 0.000116. 0.000116<0.05.This means that students in all the rows do not consume an amount of alcohol.

## When significant follow up with TukeyHSD  

```{r}
plot(TukeyHSD(model1))
```


# Discussion and Conclusion


