---
title: "Alcohol vs Seat choice"
author: "Aeilani Felix"
date: "Spring 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question: Is there a difference between the alcohol consumed between the row you choose to sit in??

# Introduction 

Is the average amount consumed per week different for the different seating rows?

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows.   

# Methods 

Data is from the UCDavis.csv

We are trying to predict alcohol consumption based on row alcohol ~ Seat

Alcohol is a numeric variable 
Seat is a categorical variable 

So we use the numerical~cat helper file

# Description 
## Graphical description 

```{r}
boxplot(alcohol~Seat,data=davisdata)
```

This boxplot shows that students who sit in the back row tend to drink more.

## Numerical description


## Inferential description 


# Discussion and Conclusion

